Orientation Control System: Enhancing Aerial Maneuvers for Quadruped Robots

### 2023-01-05 answersToReviewers.tex

\section*{Comments for Reviewer 2}
\begin{itemize}
	\item \textbf{Comment 1:} \textit{'All the simulations are performed in Gazebo'. The paper must have more details related with the simulation, including a snapshot of the simulated robot in its environment.}
	\item[] \textbf{Response:} Thank you for the insightful comment. We summarized the details of the simulation in \ref{tab:pys_param}, which is incorporated to the manuscript too. Moreover, inspired by your suggestion, we attached a sequence of snapshots for the third simulation (back-flip), showing the robot in the Gazebo environment.
	\begin{table}[H] 
		\caption{Physics related parameters used for simulate the robot dynamics in Gazebo}
		\label{tab:pys_param}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\textwidth}{CC}
			\toprule
			\textbf{Parameter} & \textbf{Value} \\
			\midrule
			Step size & $0.001 \ \mathrm{s}$\\
			Real time update rate & $250$ \\
			Physics engine & Open Dynamics Engine (ODE) \\
			Solver & Quick (Projected Gauss-Seidel method)\\
			Iterations & $50$\\
			Successive Over Relaxation parameter & $1.3$\\
			Rescaling Moment of Inertia  & no \\
			Friction model & Pyramid \\		
			\bottomrule	\end{tabularx}
	\end{table} 
	\item \textbf{Comment 2:} \textit{The authors should give more details regarding the next sentence, being crucial for the paper outputs: "The robot full dynamics is modeled with Pinocchio". Currently Gazebo supports 4 physics engines: ode, bullet, simbody and dart, being the default physics engine ode. Since the simulator models the robot dynamics, why use Pinocchio software?}
	\item[] \textbf{Response:} We acknowledge that we could have made a better explanation here. We rephrased "The robot full dynamics is modeled with Pinocchio. The references for the joints of the legs are computed off-line using Crocoddyl and tracked with a proportional-derivative joint controller." with "References for the joints of the legs are computed off-line using Crocoddyl, an optimal control library for robots based on Differential Dynamic Programming (DDP) algorithms. It uses Pinocchio for fast computation of robots dynamics and their analytical derivatives. References $\bm{q}_{ref}$, $\dot{\bm{q}}_{ref}$ and $\bm{\tau}_{ref}$ for joint positions, velocities and torques are then executed on-line with a proportional-derivative joint controller:
	\begin{equation*}
	\bm{\tau}_j = \bm{K}_{p,\, j} (\bm{q}_{ref} - \bm{q}) + \bm{K}_{d,\, j} (\dot{\bm{q}}_{ref} - \dot{\bm{q}}) + \bm{\tau}_{ref}"
	\end{equation*}
	\item \textbf{Comment 3:} \textit{ Section 2 should be expanded with more citations, an describing more related works.}
	\item[] \textbf{Response:} Thank you for the suggestion. Reviewer 1 pointed out the same advise, then you could refer to the response to Comment 5 of the the previous section. 
	\item \textbf{Comment 4:} \textit{Ide for robot code development}
	\item[] \textbf{Response:} We coded the controller using Python v3.8, with the IDE Pycharm v3.2 (\url{https://www.jetbrains.com/pycharm/}). The manuscript lacks about this information because we believe that, in our work, the use of a specific IDE is not relevant.
\end{itemize}
\vspace{12 pt}

In addition to the above observations, all orthographic and grammatical errors mentioned by the reviewers have been corrected. \\
We look forward to hearing from you in due time regarding our submission and to respond to any further questions and comments you may have.
Sincerely,

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
%\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
%\appendixstart
%\appendix
%\section[\appendixname~\thesection]{}
%\subsection[\appendixname~\thesubsection]{}
%The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

%\begin{table}[H] 
%\caption{This is a table caption.\label{tab5}}
%\newcolumntype{C}{>{\centering\arraybackslash}X}
%\begin{tabularx}{\textwidth}{CCC}
%\toprule
%\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
%\midrule
%Entry 1		& Data			& Data\\
%Entry 2		& Data			& Data\\
%\bottomrule
%\end{tabularx}
%\end{table}

%\section[\appendixname~\thesection]{}
%All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

%\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{references/bibliography.bib}

%=====================================
% References, variant B: internal bibliography
%=====================================
%\begin{thebibliography}{999}
% Reference 1
%\bibitem[Author1(year)]{ref-journal}
%Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
%\bibitem[Author2(year)]{ref-book1}
%Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
% Reference 3
%\bibitem[Author3(year)]{ref-book2}
%Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
% Reference 4
%\bibitem[Author4(year)]{ref-unpublish}
%Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
% Reference 5
%\bibitem[Author5(year)]{ref-communication}
%Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
% Reference 6
%\bibitem[Author6(year)]{ref-proceeding}
%Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of presentation. In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
% Reference 7
%\bibitem[Author7(year)]{ref-thesis}
%Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
% Reference 8
%\bibitem[Author8(year)]{ref-url}
%Title of Site. Available online: URL (accessed on Day Month Year).
%\end{thebibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\end{adjustwidth}
\end{document}
